---
title: "<span style='font-size: 18px'> <span style='text-align: center'> ReMAPP Aim 2 - Projected heatmap of outcomes"
date: "Issued: `r Sys.Date()`"
output:
  pdf_document:
    toc: no
    toc_depth: 4
    number_sections: true
    latex_engine: xelatex
    keep_tex: true
  toc-title: Table of Contents
---

**Date of included data upload to Synapse: ** 2024-06-28


\tableofcontents

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_chunk$set(fig.width = 5, fig.height = 4, fig.align = "center")
library(rmarkdown)
library(knitr)
library(tidyverse)
library(wesanderson)
library(officer)
library(flextable)
library(gt)
library(VennDiagram)
library(rms)

load("derived_data/df_heat_inf.rda")
load("derived_data/df_heat_mat.rda")
load("derived_data/df_maternal.rda")

```


\newpage
```{r ratio-denom}
#calculate maximum GA during pregnancy
df_max_ga <- df_maternal %>% 
  select(MOMID, PREGID, EST_CONCEP_DATE, starts_with("M08_LBSTDAT_")) %>% 
  pivot_longer(starts_with("M08_LBSTDAT_"), 
               names_to = "visit_type", 
               values_to = "lab_date",
               names_transform = list(visit_type = function(names) {
  gsub("^M08_LBSTDAT_", "", names)
})) %>% 
  mutate(lab_date = replace(lab_date, lab_date %in% c("1905-05-05", "1907-07-07", ""), NA)) %>% 
  filter(!is.na(lab_date)) %>% 
  mutate(ga_wks = case_when(
      as.numeric(visit_type) >= 6 ~ NA_real_,
      as.numeric(visit_type) < 6 ~ as.numeric(ymd(lab_date) - ymd(EST_CONCEP_DATE))/7
    )) %>% 
  #remove NA and outliers
  filter(ga_wks > 0 & ga_wks < 43) %>% 
  group_by(MOMID, PREGID) %>% 
  #calculate max ga for each mom
  reframe(max_ga = max(ga_wks, na.rm = TRUE)) 

#sum of max ga of moms with ga info
ratio_denom <- df_max_ga  %>%  
  reframe(total_ga = sum(max_ga, na.rm = TRUE)) %>% 
  as.numeric()
```


# Projected Heatmap for Infant Outcome 

## Projected Heatmap for Infant Outcome (1600 enrollment per site)
```{r projected heatmap infant, out.width='100%'}
# Define custom colors
colors <- c("#F11B00", "#EF5703", "#EC7A05", "#E79805", "#E3B710", "#DCCB4E", 
            "#A5C2A3", "#6FB2C1") 
breaks <- c(0, 20, 40, 60, 80, 100, 200, 300, 400)
labels <- as.character(breaks)

#calculate expected sample size for all sites after data collection
exp_n_1600 = 1600*6

#ratio: expected data/current data
ratio_1600 = exp_n_1600*40/ratio_denom

#projected data
pj_heat_inf_1600 <- df_heat_inf %>% 
  mutate(pj_count_1600 = count*ratio_1600) %>% 
  filter(hb < 19)

#Create the heatmap
ggplot(pj_heat_inf_1600, aes(x = as.factor(hb), y = outcome, fill = pj_count_1600)) +
  geom_tile(color = "white") +
  labs(x = "Hemoglobin (g/dL)", y = "", 
       title = "") + #Projected event distribution assuming 1600 enrollment per site
  theme_bw() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8, angle = 0),
        axis.title = element_text(size = 9),
        title = element_text(size = 9),
        legend.position = "bottom",
        legend.text = element_text(size = 7), 
        legend.title = element_text(size = 8),
        legend.key.width = grid::unit(1.4, "cm"), 
        legend.key.height = grid::unit(0.3, "cm"),
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0), 
        plot.title = element_text(hjust = 1.1)
        ) +
    scale_fill_gradientn(
    colors = colors,
    breaks = breaks,
    labels = labels,
    values = scales::rescale(breaks),  
    name = "Projected Count"
  ) +
  coord_fixed(ratio = 1.2) +
      guides(fill = guide_colourbar(title.position = "top",
                                title.hjust = .5,
                                label.position = "bottom"))

```
* Heat map is showing the projected count of outcome if data collection completes (1600 enrolled per site)

## Projected Heatmap for Infant Outcome (2000 enrollment per site)
```{r projected heatmap infant 2000, out.width='100%'}
#customized color
colors <- c("#F11B00", "#EF5703", "#EC7A05", "#E79805", "#E3B710", "#DCCB4E", 
            "#A5C2A3", "#6FB2C1", "#0073A8") 
breaks <- c(0, 20, 40, 60, 80, 100, 200, 300, 400, 500)
labels <- as.character(breaks)

exp_n_2000 = 2000*6

#ratio: expected data/current data
ratio_2000 = exp_n_2000*40/ratio_denom

#projected data
pj_heat_inf_2000 <- df_heat_inf %>% 
  mutate(pj_count_2000 = count*ratio_2000) %>% 
  filter(hb < 19)

color_stops <- c(0, 0.02, 0.04, 0.06, 0.08, 0.1, 0.12, 0.14, 0.16, 0.18,
                 0.2, 0.22, 0.24, 0.26, 0.28, 0.3, 0.32, 0.34, 0.36, 0.38, 0.4, 0.42, 0.71, 1)

#Create the heatmap
ggplot(pj_heat_inf_2000, aes(x = as.factor(hb), y = outcome, fill = pj_count_2000)) +
  geom_tile(color = "white") +
  labs(x = "Hemoglobin (g/dL)", y = "", 
       title = "") + 
  theme_bw() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8, angle = 0),
        axis.title = element_text(size = 9),
        title = element_text(size = 10),
        legend.position = "bottom",
        legend.text = element_text(size = 7), 
        legend.title = element_text(size = 8),
        legend.key.width = grid::unit(1.6, "cm"), 
        legend.key.height = grid::unit(0.3, "cm"),
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0),
        plot.title = element_text(hjust = 1.1)
        ) +
    scale_fill_gradientn(
    colors = colors,
    breaks = breaks,
    labels = labels,
    values = scales::rescale(breaks), 
    name = "Projected Count"
  ) +
  coord_fixed(ratio = 1.2) +
      guides(fill = guide_colourbar(title.position = "top",
                                title.hjust = .5,
                                label.position = "bottom"))

```
* Heat map is showing the projected count of outcome if data collection completes (2000 enrolled per site)

# Projected Heatmap for Maternal Outcome 

## Projected Heatmap for Maternal Outcome (1600 enrollment per site)
```{r, out.width='100%'}
#customized color
colors <- c("#F11B00", "#EF5703", "#EC7A05", "#E79805", "#E3B710", "#DCCB4E", 
            "#BDC881", "#A5C2A3", "#91BAB6", "#6FB2C1", "#3A9AB2")
breaks <- c(0, 20, 40, 60, 80, 100, 200, 300, 400, 500, 600, 700)

labels <- c("0","20", "", "60", "", "100", "200", "300", "400", "500", "600", "700")

pj_heat_mat_1600 <- df_heat_mat %>% 
  mutate(pj_count_1600 = count*ratio_1600) %>% 
  add_row(hb = c(21,21,19,20,22), 
          outcome = c("Postpartum anemia at PNC6", "Postpartum anemia at PNC26", 
                      "Likelihood of depression", "Likelihood of depression", "Likelihood of depression"), 
          pj_count_1600 = c(0,0,0,0,0)) %>% 
  filter(hb < 19)

#Create the heatmap
ggplot(pj_heat_mat_1600, aes(x = as.factor(hb), y = outcome, fill = pj_count_1600)) +
  geom_tile(color = "white") +
  labs(x = "Hemoglobin (g/dL)", y = "", 
       title = "") + 
  theme_bw() +
  theme(axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 8, angle = 0),
        axis.title = element_text(size = 9),
        title = element_text(size = 10),
        legend.position = "bottom",
        legend.text = element_text(size = 7), 
        legend.title = element_text(size = 8),
        legend.key.width = grid::unit(1.7, "cm"), 
        legend.key.height = grid::unit(0.3, "cm"),
        legend.box.margin = margin(t = 0, r = 3, b = 0, l = 0),
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0),
        plot.title = element_text(hjust = 1.05)
        ) +
    scale_fill_gradientn(
    colors = colors,
    breaks = breaks,
    labels = labels,
    values = scales::rescale(breaks),  
    name = "Projected Count"
  ) +
  coord_fixed(ratio = 1.2) +
    guides(fill = guide_colourbar(title.position = "top",
                                title.hjust = .5,
                                label.position = "bottom"))

```
* Heat map is showing the projected count of outcome if data collection completes (1600 enrolled per site)

## Projected Heatmap for Maternal Outcome (2000 enrollment per site)
```{r, out.width='100%'}
#customized color
colors <- c("#F11B00", "#EF5703", "#EC7A05", "#E79805", "#E3B710", "#DCCB4E", 
            "#BDC881", "#A5C2A3", "#91BAB6", "#6FB2C1", "#3A9AB2", "#0073A8" )
breaks <- c(0, 20, 40, 60, 80, 100, 200, 300, 400, 500, 600, 700, 800)

labels <- c("0","20", "", "60", "", "100", "200", "300", "400", "500", "600", "700", "800")

pj_heat_mat_2000 <- df_heat_mat %>% 
  mutate(pj_count_2000 = count*ratio_2000) %>% 
  mutate(pj_count_2000 = ifelse(is.na(pj_count_2000), 0, pj_count_2000)) %>% 
  add_row(hb = c(21,21,19,20,22), 
          outcome = c("Postpartum anemia at PNC6", "Postpartum anemia at PNC26", 
                      "Likelihood of depression", "Likelihood of depression", "Likelihood of depression"), 
          pj_count_2000 = c(0,0,0,0,0)) %>% 
  filter(hb < 19)

#Create the heatmap
ggplot(pj_heat_mat_2000, aes(x = as.factor(hb), y = outcome, fill = pj_count_2000)) +
  geom_tile(color = "white") +
  labs(x = "Hemoglobin (g/dL)", y = "", 
       title = "", fill = "Projected Count") + 
  theme_bw() +
  theme(axis.text = element_text(size = 8),
        axis.title = element_text(size = 9),
        title = element_text(size = 10),
        legend.position = "bottom",
        legend.text = element_text(size = 7), 
        legend.title = element_text(size = 8), 
        legend.key.width = grid::unit(1.7, "cm"), 
        legend.key.height = grid::unit(0.3, "cm"),
        legend.box.margin = margin(t = 0, r = 3, b = 0, l = -1)
        ) +
    scale_fill_gradientn(
    colors = colors,
    breaks = breaks,
    labels = labels,
    values = scales::rescale(breaks)) +
  coord_fixed(ratio = 1.2) +
  guides(fill = guide_colourbar(title.position = "top",
                                title.hjust = .5,
                                label.position = "bottom"))


```
* Heat map is showing the projected count of outcome if data collection completes (2000 per site)