---
title: "Healthy Cohort Sensitivity Analysis"
date: "`r Sys.Date()`"
output:
  pdf_document:
    toc: TRUE
    toc_depth: 2
    latex_engine: xelatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE) #, out.width = "100%"
knitr::opts_chunk$set(out.width = "100%", fig.align = "center")
library(tinytex)
library(tidyverse)
library(lubridate)
library(gt)
library(naniar)
library(emo)
library(webshot2)
library(flextable)
library(officer)
library(kableExtra)
library(ggh4x)

load("derived_data/df_sensitive.rda")
load("derived_data/df_hb_long_sensitive.rda")

#crosstable format 1
tb_theme1 <- function(matrix){
  tb <- matrix %>% 
    gt(
  #show row names
  rownames_to_stub = TRUE
) %>% 
  opt_align_table_header(align = "left") %>% 
      #spanner column label
  tab_spanner(
    label = "Site",
    columns = c(-Total)
  ) %>% 
    #use one of the default theme and customize
  opt_stylize(style = 6, color = 'blue') %>% 
  #title style
    tab_style(
    style = list(
      cell_fill(color = "skyblue4"),
      cell_text(weight = "bold"),
      cell_text(v_align = "middle"),
      cell_text(color = "white")
    ),
    locations = list(
      cells_title()
    )
    ) %>% 
  #stub head, spanner column, column label style
  tab_style(
    style = list(
      cell_fill(color = "skyblue"),
      cell_text(color = "black"),
      cell_text(v_align = "middle") 
    ),
    locations = list(
      cells_stubhead(),
      cells_column_spanners(),
      cells_column_labels() 
    )
    ) %>% 
  #cell style
  tab_style(
    style = list(
      cell_fill(color = "aliceblue"),
      cell_text(v_align = "middle") 
    ),
    locations = list(
      cells_stub()
    ) 
    ) %>% 
    #column labels align center
  tab_style(
    style = list(
      cell_text(align = "center") 
    ),
    locations = list(
      cells_column_labels(columns = everything())
    )
    ) %>% 
        #table body align right
  tab_style(
    style = list(
      cell_text(align = "right") 
    ),
    locations = list(
      cells_body(columns = everything())
    ) 
    ) %>%
  fmt_markdown(columns = everything())
} 

#test table format 1
tb_flextable <- function(data, caption, seq_id, bkm) {
  tb <- qflextable(data)
  tb <- set_table_properties(
    tb, width = 0.8, layout = "autofit",
    opts_pdf = list(tabcolsep = 3)) 
  tb <- set_caption(tb,
    caption = as_paragraph(
as_chunk(caption, props = fp_text_default(font.family = "Cambria"))
),
    word_stylename = "Table Caption",
    autonum = run_autonum(seq_id = seq_id, bkm = bkm)
  )
  tb <- bold(tb, bold = FALSE, part = "header")
  tb
}

```


### Includes data from synapse last updated: {.unlisted .unnumbered}
### Pakistan : 2023-05-26 {.unlisted .unnumbered}
### Kenya : 2023-05-26 {.unlisted .unnumbered}
### Ghana : 2023-05-26 {.unlisted .unnumbered}
<!-- ### Zambia : 2023-05-26 {.unlisted .unnumbered} -->

\newpage
## **1. Sensitivity Analysis - % Eligible by Site**
```{r}
matrix_percent <- df_sensitive %>% 
  group_by(SITE) %>% 
  summarise(
    "Total participants: N" = n(),
    "Analysis 1*: n (%)" = 
      paste0(sum(eligible1 == 1, na.rm = TRUE),
" (", format(sum(eligible1 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 2*: n (%)" = 
      paste0(sum(eligible2 == 1, na.rm = TRUE),
" (", format(sum(eligible2 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 3*: n (%)" = 
      paste0(sum(eligible3 == 1, na.rm = TRUE),
" (", format(sum(eligible3 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 4*: n (%)" = 
      paste0(sum(eligible4 == 1, na.rm = TRUE),
" (", format(sum(eligible4 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 5*: n (%)" = 
      paste0(sum(eligible5 == 1, na.rm = TRUE),
" (", format(sum(eligible5 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
     "Analysis 6*: n (%)" = 
      paste0(sum(eligible6 == 1, na.rm = TRUE),
" (", format(sum(eligible6 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 7*: n (%)" = 
      paste0(sum(eligible7 == 1, na.rm = TRUE),
" (", format(sum(eligible7 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 8*: n (%)" = 
      paste0(sum(eligible8 == 1, na.rm = TRUE),
" (", format(sum(eligible8 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 9*: n (%)" = 
      paste0(sum(eligible9 == 1, na.rm = TRUE),
" (", format(sum(eligible9 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 10*: n (%)" = 
      paste0(sum(eligible10 == 1, na.rm = TRUE),
" (", format(sum(eligible10 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 11*: n (%)" = 
      paste0(sum(eligible11 == 1, na.rm = TRUE),
" (", format(sum(eligible11 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 12*: n (%)" = 
      paste0(sum(eligible12 == 1, na.rm = TRUE),
" (", format(sum(eligible12 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 13*: n (%)" = 
      paste0(sum(eligible13 == 1, na.rm = TRUE),
" (", format(sum(eligible13 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 14*: n (%)" = 
      paste0(sum(eligible14 == 1, na.rm = TRUE),
" (", format(sum(eligible14 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 15*: n (%)" = 
      paste0(sum(eligible15 == 1, na.rm = TRUE),
" (", format(sum(eligible15 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 16*: n (%)" = 
      paste0(sum(eligible16 == 1, na.rm = TRUE),
" (", format(sum(eligible16 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 17*: n (%)" = 
      paste0(sum(eligible17 == 1, na.rm = TRUE),
" (", format(sum(eligible17 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 18*: n (%)" = 
      paste0(sum(eligible18 == 1, na.rm = TRUE),
" (", format(sum(eligible18 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 19*: n (%)" = 
      paste0(sum(eligible19 == 1, na.rm = TRUE),
" (", format(sum(eligible19 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 20*: n (%)" = 
      paste0(sum(eligible20 == 1, na.rm = TRUE),
" (", format(sum(eligible20 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
     "Analysis 21*: n (%)" = 
      paste0(sum(eligible21 == 1, na.rm = TRUE),
" (", format(sum(eligible21 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 22*: n (%)" = 
      paste0(sum(eligible22 == 1, na.rm = TRUE),
" (", format(sum(eligible22 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 23*: n (%)" = 
      paste0(sum(eligible23 == 1, na.rm = TRUE),
" (", format(sum(eligible23 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 24*: n (%)" = 
      paste0(sum(eligible24 == 1, na.rm = TRUE),
" (", format(sum(eligible24 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 25*: n (%)" =
      paste0(sum(eligible25 == 1, na.rm = TRUE),
" (", format(sum(eligible25 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 26*: n (%)" =
      paste0(sum(eligible26 == 1, na.rm = TRUE),
" (", format(sum(eligible26 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 27*: n (%)" =
      paste0(sum(eligible27 == 1, na.rm = TRUE),
" (", format(sum(eligible27 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 28*: n (%)" = 
      paste0(sum(eligible28 == 1, na.rm = TRUE),
" (", format(sum(eligible28 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 29*: n (%)" = 
      paste0(sum(eligible29 == 1, na.rm = TRUE),
" (", format(sum(eligible29 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 30*: n (%)" =
      paste0(sum(eligible30 == 1, na.rm = TRUE),
" (", format(sum(eligible30 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 31*: n (%)" =
      paste0(sum(eligible31 == 1, na.rm = TRUE),
" (", format(sum(eligible31 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 32*: n (%)" =
      paste0(sum(eligible32 == 1, na.rm = TRUE),
" (", format(sum(eligible32 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 33*: n (%)" =
      paste0(sum(eligible33 == 1, na.rm = TRUE),
" (", format(sum(eligible33 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")")
  ) %>% 
  t() %>% as.data.frame() %>% 
  `colnames<-`(c(.[1,])) %>% 
  slice(-1) %>% 
  add_column(
    .after = 6,
    "Total" = df_sensitive %>% 
      summarise(
            "Total participants: N" = n(),
    "Analysis 1: n(%)" = 
      paste0(sum(eligible1 == 1, na.rm = TRUE),
" (", format(sum(eligible1 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 2: n(%)" = 
      paste0(sum(eligible2 == 1, na.rm = TRUE),
" (", format(sum(eligible2 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 3: n(%)" = 
      paste0(sum(eligible3 == 1, na.rm = TRUE),
" (", format(sum(eligible3 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 4: n(%)" = 
      paste0(sum(eligible4 == 1, na.rm = TRUE),
" (", format(sum(eligible4 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 5: n(%)" = 
      paste0(sum(eligible5 == 1, na.rm = TRUE),
" (", format(sum(eligible5 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
     "Analysis 6: n(%)" = 
      paste0(sum(eligible6 == 1, na.rm = TRUE),
" (", format(sum(eligible6 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 7: n(%)" = 
      paste0(sum(eligible7 == 1, na.rm = TRUE),
" (", format(sum(eligible7 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 8*: n (%)" = 
      paste0(sum(eligible8 == 1, na.rm = TRUE),
" (", format(sum(eligible8 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 9*: n (%)" = 
      paste0(sum(eligible9 == 1, na.rm = TRUE),
" (", format(sum(eligible9 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 10*: n (%)" = 
      paste0(sum(eligible10 == 1, na.rm = TRUE),
" (", format(sum(eligible10 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"), 
    "Analysis 11*: n (%)" = 
      paste0(sum(eligible11 == 1, na.rm = TRUE),
" (", format(sum(eligible11 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 12*: n (%)" = 
      paste0(sum(eligible12 == 1, na.rm = TRUE),
" (", format(sum(eligible12 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 13*: n (%)" = 
      paste0(sum(eligible13 == 1, na.rm = TRUE),
" (", format(sum(eligible13 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 14*: n (%)" = 
      paste0(sum(eligible14 == 1, na.rm = TRUE),
" (", format(sum(eligible14 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 15*: n (%)" = 
      paste0(sum(eligible15 == 1, na.rm = TRUE),
" (", format(sum(eligible15 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 16*: n (%)" = 
      paste0(sum(eligible16 == 1, na.rm = TRUE),
" (", format(sum(eligible16 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 17*: n (%)" = 
      paste0(sum(eligible17 == 1, na.rm = TRUE),
" (", format(sum(eligible17 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 18*: n (%)" = 
      paste0(sum(eligible18 == 1, na.rm = TRUE),
" (", format(sum(eligible18 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 19*: n (%)" = 
      paste0(sum(eligible19 == 1, na.rm = TRUE),
" (", format(sum(eligible19 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 20*: n (%)" = 
      paste0(sum(eligible20 == 1, na.rm = TRUE),
" (", format(sum(eligible20 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
     "Analysis 21*: n (%)" = 
      paste0(sum(eligible21 == 1, na.rm = TRUE),
" (", format(sum(eligible21 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")") ,
    "Analysis 22*: n (%)" = 
      paste0(sum(eligible22 == 1, na.rm = TRUE),
" (", format(sum(eligible22 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 23*: n (%)" = 
      paste0(sum(eligible23 == 1, na.rm = TRUE),
" (", format(sum(eligible23 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 24*: n (%)" = 
      paste0(sum(eligible24 == 1, na.rm = TRUE),
" (", format(sum(eligible24 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 25*: n (%)" =
      paste0(sum(eligible25 == 1, na.rm = TRUE),
" (", format(sum(eligible25 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 26*: n (%)" =
      paste0(sum(eligible26 == 1, na.rm = TRUE),
" (", format(sum(eligible26 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 27*: n (%)" =
      paste0(sum(eligible27 == 1, na.rm = TRUE),
" (", format(sum(eligible27 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 28*: n (%)" = 
      paste0(sum(eligible28 == 1, na.rm = TRUE),
" (", format(sum(eligible28 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 29*: n (%)" = 
      paste0(sum(eligible29 == 1, na.rm = TRUE),
" (", format(sum(eligible29 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 30*: n (%)" =
      paste0(sum(eligible30 == 1, na.rm = TRUE),
" (", format(sum(eligible30 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 31*: n (%)" =
      paste0(sum(eligible31 == 1, na.rm = TRUE),
" (", format(sum(eligible31 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 32*: n (%)" =
      paste0(sum(eligible32 == 1, na.rm = TRUE),
" (", format(sum(eligible32 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")"),
    "Analysis 33*: n (%)" =
      paste0(sum(eligible33 == 1, na.rm = TRUE),
" (", format(sum(eligible33 == 1, na.rm = TRUE)/n()*100, digits = 1, nsmall = 1), ")")
      ) %>% 
      t() %>% unlist()
  )
```


```{r}
#generate table
table_percent <- tb_theme1(matrix_percent) %>%
  #table title
  tab_header(
    title = md("**Sensitivity Analysis - % Eligible by Site**")
  ) %>% 
  # stubhead label
  tab_stubhead(label = "Baseline Characteristics") 

```

```{r, out.width = '100%'}
knitr::knit_print(table_percent)

```
\newpage
>

* Analysis1*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM
* Analysis2*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_PREV_MISCARR
* Analysis3*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_PREV_PRETERM_LBW
* Analysis4*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_STILLBIRTH
* Analysis5*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM,
CRIT_COMPLICATION_NEW
* Analysis6*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_PREV_MISCARR, CRIT_PREV_PRETERM_LBW, CRIT_STILLBIRTH, CRIT_COMPLICATION_NEW
* Analysis7*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA 
* Analysis8*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_PREV_MISCARR, CRIT_PREV_PRETERM_LBW, CRIT_STILLBIRTH, CRIT_COMPLICATION_NEW, CRIT_GA
* Analysis9*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA and revise height criteria to >=150cm
* Analysis10*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_PREV_MISCARR, CRIT_PREV_PRETERM_LBW, CRIT_STILLBIRTH, CRIT_COMPLICATION_NEW, CRIT_GA and revise height criteria to >=150cm
* Analysis11*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_PREV_MISCARR, CRIT_GA
* Analysis12*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_PREV_PRETERM_LBW, CRIT_GA
* Analysis13*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_STILLBIRTH, CRIT_GA
* Analysis14*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_COMPLICATION_NEW, CRIT_GA
* Analysis15*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA and revise height criteria to >=150cm
* Analysis16*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PRETERM
* Analysis17*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_LBW
* Analysis18*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_STILLBIRTH
* Analysis19*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PREV_MISCARR
* Analysis20*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PRETERM, CRIT_LBW, CRIT_STILLBIRTH, CRIT_PREV_MISCARR
* Analysis21*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA and preeclampsia/eclampsia
* Analysis22*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA and premature rupture of membranes (before labor began)
* Analysis23*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA and macrosomia (>4000g)"
* Analysis24*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA and oligohydramnios"
* Analysis25*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA and antepartum hemorrhage
* Analysis26*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA and postpartum hemorrhage"
* Analysis27*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PRETERM, CRIT_LBW, CRIT_STILLBIRTH, CRIT_PREV_MISCARR and gestational diabetes, preeclampsia/eclampsia, premature rupture of membranes (before labor began), macrosomia (>4000g), oligohydramnios, antepartum hemorrhage, postpartum hemorrhage
* Analysis28*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PRETERM, CRIT_STILLBIRTH, CRIT_PREV_MISCARR and gestational diabetes, preeclampsia/eclampsia, premature rupture of membranes (before labor began), macrosomia (>4000g), oligohydramnios, antepartum hemorrhage, postpartum hemorrhage
* Analysis29*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_STILLBIRTH, CRIT_PREV_MISCARR and gestational diabetes, preeclampsia/eclampsia, premature rupture of membranes (before labor began), macrosomia (>4000g), oligohydramnios, antepartum hemorrhage, postpartum hemorrhage 
* Analysis30*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PRETERM, CRIT_PREV_MISCARR and gestational diabetes, preeclampsia/eclampsia, premature rupture of membranes (before labor began), macrosomia (>4000g), oligohydramnios, antepartum hemorrhage, postpartum hemorrhage
* Analysis31*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PREV_MISCARR and gestational diabetes, preeclampsia/eclampsia, premature rupture of membranes (before labor began), macrosomia (>4000g), oligohydramnios, antepartum hemorrhage, postpartum hemorrhage
* Analysis32*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PREV_MISCARR and gestational diabetes, preeclampsia/eclampsia, premature rupture of membranes (before labor began), macrosomia (>4000g), oligohydramnios, antepartum hemorrhage, postpartum hemorrhage and revise height criteria to >=150cm
* Analysis33*: exclude criteria CRIT_HEMOGLOBINOPATHIES, CRIT_IRON, CRIT_INFLAM, CRIT_GA, CRIT_PREV_MISCARR, CRIT_PRETERM, CRIT_COMPLICATION_NEW and revise height criteria to >=150cm
- Note: excluding CRIT_PRETERM and CRIT_LBW together is equal to excluding original CRIT_PREV_PRETERM_LBW
- Note: All analysis above meet the criteria CRIT_UNPL_CESARIAN. 

```{r}
df_fpr <- df_hb_long_sensitive %>%
  dplyr::select(SITE, ga_wks, hb, starts_with("eligible")) %>% 
  filter(!is.na(hb) & !is.na(ga_wks))

# call package gamlss to fit FPR model
library(gamlss)

# fit a second-order FPR model
con <- gamlss.control(trace = FALSE)
fpr_mod <- gamlss(hb ~ fp(ga_wks, 2),
  sigma.fo = ~ fp(ga_wks, 2),
  data = df_fpr, control = con
)
```

\newpage

## **2. Sensitivity analysis - Fractional polynomial regression - Pakistan**

### *Compare sample under each analysis \textcolor{red}{(red line)} with all PRiSMA enrolled participants (black line) by using centile curves - (2.5, 50, 97.5)th centiles with FPR model*

```{r , fig.show="hold", out.width="100%", fig.height = 7.5, echo=FALSE, results='hide'}

# centiles
cents <- c(2.5, 50, 97.5)

# a function to plot centile curves after excluding certain site
fpr_mod_eligible <- function(s){
  
  # remove the selected site data
  dat <- df_fpr %>% filter(eval(parse(text = paste0("eligible",s,"== 1"))))
  # fit a FPR model on the rest data
  mod <- gamlss(hb ~ fp(ga_wks, 2),
                sigma.fo = ~ fp(ga_wks, 2),
                data = dat, control = con)

  x <- df_fpr$ga_wks
  # predict hemoglobin centiles by FPR model fitted on all data
  y_fpr_mod <- centiles.pred(fpr_mod,
                         xname = "ga_wks", xvalues = x,
                         type = c("centiles"), cent = cents, data = df_fpr)
  # predict hemoglobin centiles by FPR model fitted on all data excluding the site
  y_mod <- centiles.pred(mod,
                         xname = "ga_wks", xvalues = x,
                         type = c("centiles"), cent = cents, data = dat)
  # compare the centile curves
  plot(y_fpr_mod[,1], y_fpr_mod[,2],
       ylim = c(6,16),xlim = c(10,50),
       type="n",
       xlab = "Gestational Age (weeks)", ylab = "CBC Hb (g/dL)",
       main = paste0("Analysis",s))
  for(i in 2:(length(cents)+1)) {
    lines(y_fpr_mod[,1], y_fpr_mod[,i], col = "black")
    lines(y_mod[,1], y_mod[,i], col = "red")
  }
}


newpar <- par(mfrow = c(3,2), mar = par("mar") + c(0, 1, 0, 0),
              col.axis = "blue4", col = "blue4", col.main = "blue4",
              col.lab = "blue4", pch = "+", cex = 0.5, cex.lab = 1.2,
              cex.axis = 1, cex.main = 1.2)

for (z in 1:6){
  print(fpr_mod_eligible(z))
}
par(newpar)
```

\newpage

```{r , fig.show="hold", out.width="100%", fig.height = 7.5, echo=FALSE, results='hide'}
newpar <- par(mfrow = c(3,2), mar = par("mar") + c(0, 1, 0, 0),
              col.axis = "blue4", col = "blue4", col.main = "blue4",
              col.lab = "blue4", pch = "+", cex = 0.5, cex.lab = 1.2,
              cex.axis = 1, cex.main = 1.2)
for (z in 7:33){
  print(fpr_mod_eligible(z))
}

par(newpar)
```

\newpage
## **3. Fractional polynomial regression - Pakistan**

```{r centile plot, results='hide'}
# make centile plots based on the fitted FPR model
cents <- c(2.5, 5, 10, 50, 90, 95, 97.5)
fpr_mod_centile <- function(t){
  #define data
  df_fpr <- df_hb_long_sensitive  %>% 
    dplyr::select(SITE, ga_wks, hb, starts_with("eligible")) %>%
    filter(!is.na(hb) & !is.na(ga_wks)) %>% 
    filter(eval(parse(text = paste0("eligible",t,"== 1"))))

  #model
  fpr_mod <- gamlss(hb ~ fp(ga_wks, 2),
  sigma.fo = ~ fp(ga_wks, 2),
  data = df_fpr, control = con)
  
  centile1 <- centiles(fpr_mod,
  xvar = df_fpr$ga_wks, cent = cents,
  xlab = "Gestational Age (weeks)", ylab = "CBC Hb (g/dL)",
  main = paste0(
    "Analysis",t,". Centile curves using FPR model\n(2.5, 5, 10, 50, 90, 95, 97.5)th centiles"),
  bg = "transparent",
  legend = FALSE, 
  xlim = range(10,50), ylim = range(6,16),
  pch = 15, cex = 0.4, col = "lightgrey",
  col.cent = c("red", "blue", "purple", "green", "purple", "blue", "red"),
  )
legend("topright", inset = c(-0.25,0),
       legend = c(2.5, 5, 10, 50, 90, 95, 97.5), #, "WHO"
       col = c("red", "blue", "purple", "green", "purple", "blue", "red"), 
       lty = c(1,1,1,1,1,1,1,2))
}

```

```{r , fig.show="hold", out.width="100%", fig.height = 8, echo=FALSE, results='hide'}
newpar2 <- par(mfrow = c(2,1), mar=c(4, 4, 4, 7), xpd=TRUE)
for (z in 1:2){
  print(fpr_mod_centile(z))
}
par(newpar2)
```
\newpage
```{r , fig.show="hold", out.width="100%", fig.height = 8, echo=FALSE, results='hide'}
newpar2 <- par(mfrow = c(2,1), mar=c(4, 4, 4, 7), xpd=TRUE)
for (z in 3:33){
  print(fpr_mod_centile(z))
}
par(newpar2)
```
